### 2020-06-06 sc20_reviews/response.md

  * Our experiments are chosen to span the entire range of task granularities, from very efficient (large, and low overhead) to inefficient (small, and high overhead). METG naturally determines the point at which runtime overheads come to dominate application execution. What we report in the paper are empirical results: the limit of what each system can achieve. This is a lower bound, and generally, such systems will be efficient as long as tasks are at least that large. Also, as noted in the paper, clearly there are popular and widely used systems on both ends of this spectrum; therefore some classes of applications must be able to tolerate much larger task granularities.

  * For a specific example of an application where small task granularities are useful, see <https://ieeexplore.ieee.org/document/8948618>. Figure 2 shows that with a tile size of 1024 the algorithm achieves about 7 TFLOPS/s per GPU. The task executed on each tile is a straightforward matrix multiply, making it easy to determine the the FLOPS (and therefore task granularity): (2\*1024\*1024\*1024/10^9)/7000gflops = 307us.

## Reviewer 2

  * We added Section V-I. This section validates METG against time to solution. We show that it is possible to use METG, along with a single-node measurement of time to solution, to predict the strong scalability of a code (i.e., the point where it reaches 50% parallel efficiency, in terms of both time to solution, and node count). We find that we can predict time to solution (at 50% efficiency) to within a factor of 1.42X on average across 11 programming systems and 4 Task Bench configurations.

### 2020-06-06 5_evaluation.tex
Tweak wording.

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Section~\ref{subsec:scalability} for all 11
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is at most $2.15\times$ in node count
and at most $1.42\times$ in time to solution, making this an
accurate way to predict strong scaling in the 4 patterns we tested in
Section~\ref{subsec:scalability}.

>>>>

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Section~\ref{subsec:scalability} for all 11
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is at most $2.15\times$ in node count
and at most $1.42\times$ in time to solution, making this a
useful way to predict strong scaling in the 4 patterns we tested in
Section~\ref{subsec:scalability}.
